---
title: "Graduate Project"
author: "Mary McBride"
date: "2020-04-24"
output: html_document
---

### Load packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
library(tidymodels)
```


I was able to find a data set on kaggle that included reviews and ratings for online recipies. I am trying to predict what the rating will be based on the number of characters in a review. My prediciton is that a longer review will lead to worse ratings. 

Prediciton question: Does a longer review mean that someone left a worse rating? 

To test my prediciton I will be making a decision tree. This way I can see what the cut off points are for each rating.


First, I needed to add another column to my data set to count the number of characters in the review. 
Next, I split the data and did cross validation on the training data, which will be used later. 





```{r getting data ready}
set.seed(7)
rec <- read_csv("rec.csv")

rec$noChar <- nchar(rec$Review)

```


```{r crossval}


set.seed(7)
rec_split <- initial_split(rec, prop = 0.5)
rec_train <- training(rec_split)


rec_cv <- vfold_cv(rec_train , v = 10)
```





```{r tune}
tree_spec <- decision_tree(
  cost_complexity = tune(), 
  tree_depth = 10,
  mode = "regression") %>%
  set_engine("rpart")



grid <- expand_grid(cost_complexity = seq(0, 100, by = 10))
model <- tune_grid(tree_spec,
                   Rating ~ noChar,
                   grid = grid,
                   resamples = rec_cv)




model %>%
  collect_metrics() %>%
  filter(.metric == "rmse") %>%
  arrange(mean)

```























